Tutorial_4

### 2024-12-04 Tutorial_4.Rmd
updated Tutorial 4

1. Fit a regression model to an existing dataset.
2. Use the regression model parameters to simulate a one new dataset.
3. Create a function to iterate over many datatsets and vary parameters of interest (e.g., sample size, trial count, effect size).
4. Summarise the simulated data to estimate likely power or precision of the research design options.

@@

ggsave ("Tutorial_4_planning/figures/raw_vs_d1.jpeg",
        width = 8, height = 8)
```

@@

```{r sim1-power-col}
p10.4 <- ggplot(power_x1, aes(x=rep_n, y=power,
                           colour = b6c, fill = b6c)) +
  geom_col(alpha = 0.5) +
  geom_hline(yintercept = 0.8, colour = "red", linetype = "dashed") +
  geom_hline(yintercept = 0.9, colour = "black", linetype = "dashed") +
  geom_hline(yintercept = 0.95, colour = "blue", linetype = "dashed") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  facet_wrap(~b6c, nrow=1)
p10.4

@@

```{r sim2-power-col}
p11.6 <- ggplot(power_x2, aes(x=subj_n, y=power,
                           colour = b6c, fill = b6c)) +
  geom_col(alpha = 0.5) +
  geom_hline(yintercept = 0.8, colour = "red", linetype = "dashed") +
  geom_hline(yintercept = 0.9, colour = "black", linetype = "dashed") +
  geom_hline(yintercept = 0.95, colour = "blue", linetype = "dashed") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  theme(legend.position = "none") +
  facet_wrap(~b6c, nrow=1)
p11.6

@@

>>>>

1. Fit a regression model to an existing dataset.
2. Use the regression model parameters to simulate one new dataset.
3. Write a function to create 1000s of datasets and vary parameters of interest (e.g., sample size, trial count, effect size).
4. Summarise the simulated data to estimate likely power or precision of the research design options.

@@

ggsave ("Tutorial_4_planning/figures/raw_vs_d1.jpeg",
        width = 8, height = 8, dpi=800)
```

@@

```{r sim1-power-col}
p10.4 <- ggplot(power_x1, aes(x=rep_n, y=power,
                           colour = b6c, fill = b6c)) +
  geom_col(alpha = 0.5) +
  geom_hline(yintercept = 0.8, colour = "red", linetype = "dashed") +
  geom_hline(yintercept = 0.9, colour = "black", linetype = "dashed") +
  geom_hline(yintercept = 0.95, colour = "blue", linetype = "dashed") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "Simulation 1") +
  theme(legend.position = "none") +
  facet_wrap(~b6c, nrow=1)
p10.4

@@

```{r sim2-power-col}
p11.6 <- ggplot(power_x2, aes(x=subj_n, y=power,
                           colour = b6c, fill = b6c)) +
  geom_col(alpha = 0.5) +
  geom_hline(yintercept = 0.8, colour = "red", linetype = "dashed") +
  geom_hline(yintercept = 0.9, colour = "black", linetype = "dashed") +
  geom_hline(yintercept = 0.95, colour = "blue", linetype = "dashed") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "Simulation 2") +
  theme(legend.position = "none") +
  facet_wrap(~b6c, nrow=1)
p11.6

@@

# 12. Join some plots together #

Join the power column plots together from sim1 and sim2.

```{r}
p12.1 <- (p10.4 | p11.6) +
  plot_annotation(tag_levels = 'A') +
  plot_layout(axes = 'collect')
p12.1

ggsave ("Tutorial_4_planning/figures/bin6_power_col.jpeg",
        width = 12, height = 7, dpi=800)
```
